Test a simpler version of veb-boost performance mr.ash2s on ukbiobank data

### 2020-08-12 analysis/simulation-mr.ash2s-ukbchr22-gtex.adipose.Rmd
twas summarize

MR.ASH results (start from gene):
```{r sim 5 gene, out.width = "98%", out.height="95%"}
tag <- "20200616-5"
tag2 <- "expr-res"

@@

MR.ASH results (start from gene):
```{r sim 6 gene, out.width = "98%", out.height="95%"}
tag <- "20200616-6"
tag2 <- "expr-res"

@@

MR.ASH results (use lasso for all):
```{r sim 7 lasso, out.width = "98%", out.height="95%", eval = T}
tag <- "20200616-7"
tag2 <- "lasso"

@@

MR.ASH results (use lasso for just for SNPs):
```{r sim 7 lassosnp, out.width = "98%", out.height="95%", eval = T}
tag <- "20200616-7"
tag2 <- "lassoSNP"

@@

MR.ASH results (use lasso for all):
```{r sim 8 lasso, out.width = "98%", out.height="95%", eval = T}
tag <- "20200616-8"
tag2 <- "lasso"

@@

MR.ASH results (use lasso for just for SNPs):
```{r sim 8 lassosnp, out.width = "98%", out.height="95%", eval = T}
tag <- "20200616-8"
tag2 <- "lassoSNP"

@@

>>>>

MR.ASH results (start from gene):
```{r sim 5 gene, out.width = "98%", out.height="95%", eval = F}
tag <- "20200616-5"
tag2 <- "expr-res"

@@

MR.ASH results (start from gene):
```{r sim 6 gene, out.width = "98%", out.height="95%", eval = F}
tag <- "20200616-6"
tag2 <- "expr-res"

@@

MR.ASH results (use lasso for all):
```{r sim 7 lasso, out.width = "98%", out.height="95%", eval = F}
tag <- "20200616-7"
tag2 <- "lasso"

@@

MR.ASH results (use lasso for just for SNPs):
```{r sim 7 lassosnp, out.width = "98%", out.height="95%", eval = F}
tag <- "20200616-7"
tag2 <- "lassoSNP"

@@

### MR.ASH results (use lasso for all):
```{r sim 8 lasso, out.width = "98%", out.height="95%", eval = F}
tag <- "20200616-8"
tag2 <- "lasso"

@@

### MR.ASH results (use lasso for just for SNPs):
```{r sim 8 lassosnp, out.width = "98%", out.height="95%", eval = F}
tag <- "20200616-8"
tag2 <- "lassoSNP"

@@

### More examples from separate runs: 
```{r sim 20200616-8-7, out.width = "98%", out.height="95%"}
source("analysis/visual_twas_plots.R")
tag <- "20200616-8-7"
tag2 <- "lassoes-es"
f <- get_files(tag= tag, tag2 = tag2)
param <- read.table(f$par, header = T, row.names = 1)
print(param)
```
```{r 20200616-8-7, out.width = "98%", out.height="95%"}
plot_all(f$gmrash, f$ggwas, f$smrash, f$sgwas, f$gsusie, f$ssusie, f$rsq)
```
